---
title: "Data Cleaning Project"
author: Rajeev Kumar
date: 04/28/2018
output: html_document
---

## Setting up working directory
```{r}
library("data.table")
setwd("C:/Data Science/Data cleaning/Project")
```

## Installing Data.Table package and setting up the working directory
```{r}
trnX<-read.table("X_train.txt")
trnY<-read.table("y_train.txt")
tstX<-read.table("X_test.txt")
tstY<-read.table("y_test.txt")

subtst<-read.table("subject_test.txt")
subtrn<-read.table("subject_train.txt")

lblact<-read.table("activity_labels.txt")
fture<-read.table("features.txt")
```

## Merging training and test datasets
```{r}
merge_x<-rbind(tstX,trnX)
merge_y<-rbind(tstY,trnY)
merge_sub<-rbind(subtst,subtrn)
```

## Identifying columns only for mean and standard deviation from feature database
```{r}
sel_col<-grep("mean\\(\\)|std\\(\\)",fture[,2])
merge_scol<-merge_x[,sel_col]
```

## Using descriptive activity names to name the activities in the data set
```{r}
Activity_ID<-lblact[merge_y[,1],2]
```

## Appropriately labels the data set with descriptive variable names.
```{r}
names(merge_scol)<-fture[sel_col,2]
names(merge_sub)<-"Subject_ID"
fdata<-cbind(merge_sub, Activity_ID,merge_scol)
```

## Calculating mean and STD by Subject ID and Activity ID
```{r}
fdata<-data.table(fdata)
sd_avg <- fdata[,lapply(.SD,mean), by = 'Subject_ID,Activity_ID']
```

## Writting dataset to the file
```{r}
write.table(sd_avg,"tidydataset.txt",row.names = FALSE)
```